Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\ Through Sub-sampling and Reconstruction

### 2019-06-28 latex/afm-cs-main.tex
Double period.

For raster scanning, we set $F_X=F_Y=1$ and instead take advantage of
the periodicity of the $X$-axis reference, which is a triangle wave.
We modify the triangle wave to a truncated Fourier series, where each
Fourier coefficient is scaled by the inverse of the closed-loop FRF at
the corresponding frequency. See, e.g., \cite{clayton_review_2009} for
more details on this strategy. We truncate this series such that the
highest frequency is smaller than 200 Hz, which means that we should
never excite the problematic $G_{Z,u_X}$ modes. This scheme implies
that the effective bandwidth of the $X$-axis controller is higher
while raster scanning than while CS-scanning. On the other hand, it
also implies that for faster scan rates, fewer Fourier
coefficients are used, and so the approximation to a triangle wave is
worse, leading to scans which do not cover the entire intended range..

>>>>

For raster scanning, we set $F_X=F_Y=1$ and instead take advantage of
the periodicity of the $X$-axis reference, which is a triangle wave.
We modify the triangle wave to a truncated Fourier series, where each
Fourier coefficient is scaled by the inverse of the closed-loop FRF at
the corresponding frequency. See, e.g., \cite{clayton_review_2009} for
more details on this strategy. We truncate this series such that the
highest frequency is smaller than 200 Hz, which means that we should
never excite the problematic $G_{Z,u_X}$ modes. This scheme implies
that the effective bandwidth of the $X$-axis controller is higher
while raster scanning than while CS-scanning. On the other hand, it
also implies that for faster scan rates, fewer Fourier
coefficients are used, and so the approximation to a triangle wave is
worse, leading to scans which do not cover the entire intended range.
